SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-27 scipy-1.0/covlett.tex
Update scipy-1.0/covlett.tex
Co-Authored-By: Matt Haberland <mdhaber@mit.edu>
MAINT: PR 193 reviewer comments
* reduce side margins in cover letter

* remove end-of-line commas in address
/ contact blocks & do not place "USA"
on its own line

* reformat justificatio paragraph from
Matt H's suggestion & a few more
adjustments to fit letter on single page

% to adjust vertical spacing properties of
% newlfm class see: https://tex.stackexchange.com/a/65533/43006
%\unprtop{0mm}
\topmarginsize{0mm}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}
\MinHead{0in}
%\dateskipafter{0pt}
%\dateskipbefore{0pt}
%\sigskipbefore{0pt}
%\sigskipafter{0pt}
\closeskipbefore{1pt}
%\closeskipafter{0pt}
%\addrfromskipbefore{0pt}
\addrfromskipafter{0in}
\addrtoskipbefore{0in}
%\addrtoskipafter{0pt}
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
\newlfmP{sigsize=10pt}
\bottommarginskip{0pt}
\MinFoot{0pt}

\usepackage{kpfonts}
\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

\namefrom{Ralf Gommers,
          Matt Haberland,
          and Tyler Reddy}
\addrfrom{%
    \today\\[10pt]
    Ralf Gommers,\\
    Quansight Labs,\\
    The Netherlands,\\
    \texttt{ralf.gommers@gmail.com},\\
    %phone number\\
    \\
    Matt Haberland,\\
    BioResource and Agricultural Engineering,\\
    California Polytechnic State University,\\
    San Luis Obispo, CA, 93407, USA,\\
    \texttt{mhaberla@calpoly.edu},\\
    %phone number\\
    \\
    Tyler Reddy,\\
    CCS-7 Applied Computer Science Group,\\
    Los Alamos National Laboratory,\\
    Los Alamos, NM, 87545, USA,\\
    \texttt{treddy@lanl.gov},\\
    %phone number\\
}

\addrto{%
Dr. Rita Strack,\\
Nature Methods Editorial Office,\\
One New York Plaza Suite 4500,\\
New York, NY 10004,\\
USA}

@@

We have specifically chosen \emph{Nature Methods} because
SciPy lies at the base of the entire ecosystem of scientific methods
described in the journal scope, and because SciPy is effectively an
ever-improving methodological library. High-profile manuscripts citing SciPy 
extend beyond the biosciences to recent reports on gravitational waves and
black holes. Lacking a better alternative, these citations all point
to the SciPy website; instead, we think the package now merits a
formal publication in a highly visible journal. A pre-print will likely
soon be made available on arXiv.

@@

Thank you for your consideration.  We look forward to
    hearing from you.\vspace*{0.1cm}
\end{newlfm}
\end{document}

>>>>

% to adjust vertical spacing properties of
% newlfm class see: https://tex.stackexchange.com/a/65533/43006
%\unprtop{0mm}
\topmarginsize{0mm}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}
\MinHead{0in}
%\dateskipafter{0pt}
%\dateskipbefore{0pt}
\sigskipbefore{40pt}
%\sigskipafter{0pt}
\closeskipbefore{1pt}
%\closeskipafter{0pt}
%\addrfromskipbefore{0pt}
\addrfromskipafter{0in}
\addrtoskipbefore{0in}
%\addrtoskipafter{0pt}
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
\newlfmP{sigsize=10pt}
\bottommarginskip{10pt}
\MinFoot{0pt}
\leftmarginsize{0.95in}
\rightmarginsize{0.95in}

\usepackage{kpfonts}
\usepackage{hyperref}
\usepackage{url}

\hypersetup{%
  linkbordercolor=blue,% hyperlink borders will be blue
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}
\widowpenalty=1000
\clubpenalty=1000

\namefrom{Ralf Gommers,
          Matt Haberland,
          and Tyler Reddy}
\addrfrom{%
    \today\\[10pt]
    Ralf Gommers\\
    Quansight Labs\\
    The Netherlands\\
    \texttt{ralf.gommers@gmail.com}\\
    %phone number\\
    \\
    Matt Haberland\\
    BioResource and Agricultural Engineering\\
    California Polytechnic State University\\
    San Luis Obispo, CA, 93407, USA\\
    \texttt{mhaberla@calpoly.edu}\\
    %phone number\\
    \\
    Tyler Reddy\\
    CCS-7 Applied Computer Science Group\\
    Los Alamos National Laboratory\\
    Los Alamos, NM, 87545, USA\\
    \texttt{treddy@lanl.gov}\\
    %phone number\\
}

\addrto{%
Dr. Rita Strack\\
Nature Methods Editorial Office\\
One New York Plaza Suite 4500\\
New York, NY 10004, USA}

@@

SciPy lies at the base of the ecosystem of life science computational
methods. Many studies, including an extremely influential \emph{Nature 
Methods} paper (\href{https://www.nature.com/articles/nmeth.f.303}
{Caporaso \emph{et al.}~2010}), describe software that 
includes SciPy as a dependency without citing it. Others in \emph{
Nature Methods} (e.g.,\href{https://www.nature.com/articles/s41592-018-0114-z}{
Gruber \emph{et al.}~2018};\href{https://www.nature.com/articles/s41592-019-0403-1}{
Moen \emph{et al.}~2019}) -- and some 3000+ other articles -- 
cite SciPy's website for lack of
a better alternative. As SciPy is central to so many biological studies,
the research community would benefit from an article about SciPy to reference.
Our preprint \href{https://arxiv.org/abs/1907.10121}{available on arXiv} 
only partially fulfills this need; we appreciate your consideration of
the manuscript for publication in \emph{Nature Methods}.

@@

\end{newlfm}
\end{document}
